%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://aroraakshit.github.io/}{\Large Akshit Arora}} & \href{mailto:akshit.arora@colorado.edu}{akshit.arora@colorado.edu} \\
  \href{https://aroraakshit.github.io/}{https://aroraakshit.github.io/} & +1 (720) 618-7199 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Colorado}{Boulder, CO}
      {Master of Science in Computer Science (Specialization: Artificial Intelligence)}{Aug. 2017 -- Present}
    \resumeSubheading
      {Thapar University}{Patiala, India}
      {Bachelor of Engineering in Computer Engineering; GPA: 3.67 (Major), 3.37 (Overall)}{Aug. 2013 -- Jul. 2017}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}{Python, C++, SQL, PHP, C\# \hfill \textbf{Technologies}: Tensorflow, Unity 3D, Vuforia, Bootstrap}
    \resumeSubItem{Graduate Courses}{Neural Networks \& Deep Learning; Design \& Analysis of Algorithms}
    
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {University of Colorado}{Boulder, CO}
      {Grader and Teaching Assistant at the Department of Computer Science}{Aug 2017 - Present}
      \resumeItemListStart
        \resumeItem{Teaching Assistant - The Art of Computational Thinking}
          {An introductory course on python with more than 200 students enrolled. Responsible for conducting lab sessions, holding office hours and prepare assignments.}
        \resumeItem{Grader - Human-Centered Computing Foundations}
          {An introduction to current practices and research in human-centered computing with more than 150 students enrolled. Involved in grading assignments.}
      \resumeItemListEnd

    \resumeSubheading
      {Indian Institute of Technology (IIT), Mandi}{Himachal Pradesh, India}
      {Research Intern at the Applied Cognitive Science Lab}{Jun 2014 - Jul 2017}
      \resumeItemListStart
        \resumeItem{Interactive Landslide Simulator (ILS)}
          {A web-based research tool to balance public risk perceptions and how people at risk could adapt to and mitigate the landslides in their neighbourhood.  \href{http://pratik.acslab.org/}{http://pratik.acslab.org/}}
        \resumeItem{Marker-based and GPS-based Augmented Reality (AR)}
          {A tool for training military personnel in different cognitive loads. Responsible for making AR simulations similar to scavenger hunt and first-person-shooter games.}
         \resumeItem{Monitoring physiological sensors in real-time}
          {Integrated sensors for measuring blood pressure, galvanic skin response, heart rate and respiration (by NeuLog) to the AR simulations for military personnel.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects And Publications}
  \resumeSubHeadingListStart
  \resumeSubItem{Intelligent Virtual Assistant}
    {(Ongoing) A chat-bot for motivation quotes on facebook's messenger.\newline \textbf{Using: Tensorflow, api.ai, Python}}
    \resumeSubItem{Student Evaluation Portal}
      {A tool to track and evaluate student's performance over 6 months training period.\newline \textbf{Using: CodeIgniter, Google Analytics, MySQL, KAdmin}; Worked in a team of 4; Link: \href{https://goo.gl/zZuCTv}{goo.gl/zZuCTv} }
     \resumeSubItem{\href{https://www.researchgate.net/publication/319471329_Learning_in_an_Interactive_Simulation_Tool_against_Landslide_Risks_The_Role_of_Amount_and_Availability_of_Experiential_Feedback}{\textbf{Learning in an Interactive Simulation Tool against Landslide Risks: The Role of Amount and Availability of Experiential Feedback}}}
          {Chaturvedi P, \textbf{\underline{Arora A}}, Dutt V. Natural Hazards and Earth System Sciences. 10.5194/nhess-2017-297. Sep 2017. \textbf{Journal Paper}.}
    \resumeSubItem{\href{http://link.springer.com/chapter/10.1007/978-3-319-41627-4_21}{\textbf{Interactive Landslide Simulator: A Tool for Landslide Risk Assessment and Communication}}} {Chaturvedi P, \textbf{\underline{Arora A}}, Dutt V. Advances in Applied Digital Human Modeling and Simulation (Springer Books). 481: 231-243. Jul 2016. \textbf{Book Chapter}.}
    \resumeSubItem{\href{http://www.ahfe2016.org/}{\textbf{Interactive landslide simulator: A tool for landslide risk and damage assessment.} }}
    {Chaturvedi P, \textbf{\underline{Arora A}} and Dutt V. Applied Human Factors and Ergonomics, Orlando, Florida, USA. Jul 2016. \textbf{Oral Presentation}.}
    %\resumeSubItem{Room Allocation System}
    %  {Application for resident hall to manage room allocation for 1000+ incoming students. \newline \textbf{Using: Bootstrap, CodeIgniter, MySQL}; Worked in a team of 2}
    \resumeSubItem{Ph.D. records management}
      {Manage information (like \%Ph.D. completion, publications, etc) of Ph.D. students.\newline \textbf{Using: Bootstrap, PHP, MySQL}; Worked in a team of 3; Link: \href{https://goo.gl/Rt2zXt}{goo.gl/Rt2zXt}}
  \resumeSubHeadingListEnd
 
  
%-----------OTHER ACTIVITIES-----------------
\section{Leadership Activities and Awards}
  \resumeSubHeadingListStart
  \resumeSubItem{Travel Fellowship Award}
      {by Thapar University and IIT Mandi; for presenting 3 research papers at 7th International Conference on Applied Human Factors and Ergonomics.}
  \resumeSubItem{Co-Convener - International Forum for Leadership and Sustainability}
    {Organized awareness campaigns, quiz events, dog vaccination camps and creativity competitions for underprivileged students.}
    \resumeSubItem{Photography Events}
      {Organized photo-walks in IIT Mandi and Thapar University. Encouraged different types of photography. Regularly update photos at 500px. (\href{https://500px.com/akshitarora}{Link: 500px.com/akshitarora})}
      
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
